---
title: "Report on the Coffee Co-op"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

```{r echo=FALSE,message=FALSE}
library(knitr)
library(knitr)
library(ggplot2)
library(lubridate)
opts_chunk$set(message=FALSE,warning=FALSE,echo=FALSE,dev="pdf",cache=TRUE)

info <- read.csv("../coffee_database/info.csv", stringsAsFactors = FALSE)
consumption <- read.csv("../coffee_database/consumption.csv", stringsAsFactors = FALSE)
donations <- read.csv("../coffee_database/donations.csv", stringsAsFactors = FALSE)
consumption2 <- add_donation(consumption, donations, 1)
accounts <- read.csv("../SignupSheet/accounts_active.csv", stringsAsFactors = FALSE)

info$Date <- ymd(info$Date)
consumption2$Date <- ymd(consumption2$Date)
```

# Report on the state of the Coffee Co-op
```{r}
since_last <- difftime(info$Date[length(info$Date)],info$Date[length(info$Date)-1],units="days")
consumed_coffees <- info$Count[length(info$Count)]-info$Count[length(info$Count)-1]
marked_coffees <- consumption2 %>%
  group_by(Date) %>%
  summarise(tot_coffee = sum(Coffee)) %>%
  tail(1)
```

It has been `r since_last[[1]]` days since our sheet was updated. In that time we drank **`r consumed_coffees` coffees**, of which **`r marked_coffees$tot_coffee`** were marked down; making our honesty during this period **`r round(100*marked_coffees$tot_coffee/consumed_coffees)`%**

## The distribution of co-op balances:
Among users currently present in the building, **`r round(sum(accounts$balance<0)/nrow(accounts)*100)`%** owe the co-op money, representing a total debt of **`r sum(accounts$balance[accounts$balance<0],na.rm=TRUE)`**.

**Please come and pay Ken (236).  Let's try to improve these numbers!**

## Balance 


```{r fig.cap="The distribution of balances"}
dd <- with(density(accounts$balance),data.frame(x,y))

ggplot(data = dd, mapping = aes(x = x, y = y)) +
geom_line(color="black") + geom_polygon(data = dd, aes(x=ifelse(x < 0,x,0), y=y))+scale_y_continuous(limits = c(0,max(dd$y)), name="Density") +
scale_x_continuous(name="Balance ($)")

```