---
title: "Donations of the Coffee Co-op"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---


```{r echo=FALSE,message=FALSE}
library(knitr)
library(knitr)
library(ggplot2)
library(lubridate)
opts_chunk$set(message=FALSE,warning=FALSE,echo=FALSE,dev="pdf",cache=TRUE)
```

# Report on the donations from the Coffee Co-op
```{r}
extra_donations <- read.csv("../coffee_database/extra_donations.csv", stringsAsFactors = FALSE)
donations <- read.csv("../coffee_database/donations.csv", stringsAsFactors = FALSE)
info <- read.csv("../coffee_database/info.csv", stringsAsFactors = FALSE)
```

```{r}

info <- read.csv("../coffee_database/info.csv", stringsAsFactors = FALSE)
consumption <- read.csv("../coffee_database/consumption.csv", stringsAsFactors = FALSE)
donations <- read.csv("../coffee_database/donations.csv", stringsAsFactors = FALSE)

extra_donations_total <- extra_donations %>%
  group_by(Date) %>%
  summarise(donated = sum(extra_donated))
```


```{r}
total_donations <- calculate_donations(donations, info) %>% 
  select(collected_total) %>% 
  tail(1)
Coffees <- calculate_donations(donations, info) %>% 
  select(coffees_drank) %>% 
  tail(1)
```

```{r}
final_donations <- extra_donations_total$donated + total_donations$collected_total
```

```{r}
date <- info %>%
  select(Date) %>%
  slice((nrow(info)-1)) %>%
  ymd() 
month_don <- month(date, label = TRUE, abbr = FALSE)
day_don <- day(date)
```

Congratulations everyone! Since `r day_don` `r month_don` we collected **$`r final_donations`** for the AMS food bank. We had **$`r extra_donations_total$donated`** directly donated and **$`r total_donations$collected_total`** in `r Coffees` coffees. 

Please thank Matt Siegle for the intitiative!

Keep up the drinking! 

The coffee co-op is now set up to accept donations through direct donation or by marked coffees. If you are interested in setting up a donation event please contact Melissa in office 207. 

