---
title: "Donations of the Coffee Co-op"
author: "Melissa Guzman"
date: "February 17, 2016"
output: pdf_document
---


```{r echo=FALSE,message=FALSE}
library(knitr)
library(ggplot2)
library(lubridate)
opts_chunk$set(message=FALSE,warning=FALSE,echo=FALSE,dev="pdf")

```

# Report on the state of the Coffee Co-op
```{r}
since_last <- difftime(info$Date[length(info$Date)],info$Date[length(info$Date)-1],units="days")
marked_coffees <- sum(donations[which(donations$data_date==max(donations$Date)),"Coffee"])

total_donations
```

It has been `r since_last[[1]]` days since our sheet was updated. In that time we drank **`r consumed_coffees` coffees**, of which **`r marked_coffees`** were marked down; making our honesty during this period **`r round(100*marked_coffees/consumed_coffees)`%**

## The distribution of co-op balances:
Among users currently present in the building, **`r round(sum(accounts$balance<0)/nrow(accounts)*100)`%** owe the co-op money, representing a total debt of **`r sum(accounts$balance[accounts$balance<0],na.rm=TRUE)`**.

