```{r echo=FALSE,message=FALSE}
opts_chunk$set(message=FALSE,warning=FALSE,echo=FALSE,dev="pdf")
```

```{r}
library(ggplot2)
source("merge_organize_coop_data.R")

```

# Report on the state of the Coffee Co-op
```{r}
since_last <- difftime(info$Date[length(info$Date)],info$Date[length(info$Date)-1],units="days")
consumed_coffees <- info$Count[length(info$Count)]-info$Count[length(info$Count)-1]
marked_coffees <- sum(consumption[which(consumption$data_date==max(info$Date)),"Coffee"])
```

It has been `r since_last[[1]]` days since our sheet was updated. In that time we drank **`r consumed_coffees` coffees**, of which **`r marked_coffees`** were marked down; making our honesty during this period **`r round(100*marked_coffees/consumed_coffees)`%**

## The distribution of co-op balances:
Among users currently present in the building, **`r round(sum(accounts_alphabet$balance<0)/nrow(accounts_alphabet)*100)`%** owe the co-op money, representing a total debt of **`r sum(accounts_alphabet$balance[accounts_alphabet$balance<0],na.rm=TRUE)`**. If we consider all users **EVER** in the co-op, the total debt is **`r sum(accounts_pres$balance[accounts_pres$balance<0],na.rm=TRUE)`**.

**Please come and pay Andrew MacDonald (203).  Let's try to improve these numbers!**

## milk consumption
we drank `r with(subset(costnumbers,costnumbers$data_date==max(costnumbers$data_date)),sum(Milk))` milks, which altogether cost us `r with(subset(costnumbers,costnumbers$data_date==max(costnumbers$data_date)),sum(Milk*CostMilk))`.

```{r fig.cap="The distribution of balances"}
dd <- with(density(accounts_alphabet$balance),data.frame(x,y))

ggplot(data = dd, mapping = aes(x = x, y = y)) +
geom_line(color="black") + geom_polygon(data = dd, aes(x=ifelse(x < 0,x,0), y=y))+scale_y_continuous(limits = c(0,max(dd$y)), name="Density") +
scale_x_continuous(name="Balance ($)")

```
